Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
Autre formule.
...

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

@@

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}

@@

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum}
		\label{asumsum}
		\begin{algorithmic}
		\Require{}
		\Statex
		\While{step < I}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

@@

	generalisation to multiple activities per cluster :

@@

@@

@@

	\newpage
	%$\,$
	%\newpage
	\begin{figure}
		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}

	Absolute values of slopes diminish for increasing number of activities (resilience is better)

@@

	$\eta_\psi = max_x \eta_{x, \psi}$

>>>>

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

@@

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}

@@

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum \label{asumsum}}

		\begin{algorithmic}
		\Require{}
		\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-(\frac{1}{{l \choose a}})^{c - c_e})^{-(m-1)}$
	%\frac{c}{(c-c_e) \log_2{l \choose a }}

@@

	Generalisation to multiple activities per cluster :

	For example an \textbf{a}ctivated \textbf{g}ood neuron in a \textbf{c}orrect cluster starts with a base score of $ a(c - c_e - 1) + \gamma$. The probability it has to be connected to a random activated neuron in an erroneous cluster is $d$. Thereby its law is :

@@

	The other laws are also easily expressed :

@@

		$\eta_m = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times \left [\sum_{k = c_e+1}^{c} \left (1-\frac{1}{{l \choose a}} \right )^k \left (\frac{1}{{l \choose a}} \right )^{c-k} \right ] ^{-(m-1)}$

@@

	\newpage
	%$\,$
	%\newpage
	\begin{figure}

		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
	\end{figure}

	We compute values represented on figure \ref{comppsi} by scanning on the number of messages, so as to find the maximum efficiency.

	After a transition, efficiencies seem to follow a linear decreasing low according to $\psi$.

	Absolute values of slopes diminish for increasing number of activities per cluster. We can conclude multipartite cliques improve the resilience of the network.

@@

	$\eta_\psi = max_x \, \eta_{x, \psi}$
